The contributions of the work done for this thesis are summarised:
\begin{itemize}
    \item We designed a high-fidelity simulation environment, which was open-sourced for public use with an MIT Licence at the linked \href{https://github.com/NUIG-ROCSAFE/CBRNeVirtualEnvironment/releases}{Github repository.}\footnote{\href {https://github.com/NUIG-ROCSAFE/CBRNeVirtualEnvironment/releases}{https://github.com/NUIG-ROCSAFE/CBRNeVirtualEnvironment/releases}} The development of the simulation environment is discussed in Chapter \ref{chap:HighFidelitySim}.
    \item We designed and open-sourced a software framework to solve the problem of target detection in a hazardous environment. The software implementation can be found at the linked 
    \href{https://github.com/DavidLSmyth/OccupancyGridAgent}{repository on Github.}\footnote{\href {https://github.com/DavidLSmyth/OccupancyGridAgent}{https://github.com/DavidLSmyth/OccupancyGridAgent}} The details related to the implemented solution can be found in Chapter \ref{chap:targetLocalisation}.
    \item We designed and open-sourced software that can generate routes for multiple agents to cover a uniformly-spaced grid according to various objective functions. The software implementation can be found at the linked 
    \href{https://github.com/DavidLSmyth/CBRNeMissionDesigner}{repository on Github.}\footnote{\href {https://github.com/DavidLSmyth/CBRNeMissionDesigner}{https://github.com/DavidLSmyth/CBRNeMissionDesigner}}
    \item We designed and open-sourced a user interface which allows the user to specify the bounding points of a polygonal region using the WGS84 coordinate system. Using the grid generation  software, the user can generate a grid over this region. Using the agent-routing software it is then possible to request for routes be generated for multiple agents to execute in a real or virtual environment. If the virtual environment developed above is chosen, the user can optionally request for data-gathering tasks be carried out while visiting each grid point. The integrated software implementation can be found at the linked \href{https://github.com/NUIG-ROCSAFE/CBRNeVirtualEnvironment/}{Github repository.}\footnote{\href {https://github.com/NUIG-ROCSAFE/CBRNeVirtualEnvironment/}{https://github.com/NUIG-ROCSAFE/CBRNeVirtualEnvironment/}}
\end{itemize}

Publications related to this research are listed:
\begin{enumerate}
    \item \bibentry{Smyth2018AInvestigation}
    \item \bibentry{Smyth2018UsingDrones}
    \item \bibentry{Smyth2018ASupport}

\end{enumerate}