%!TEX root = ../thesis.tex
%*******************************************************************************
%****************************** Literature review chapter *********************************
%*******************************************************************************


\chapter{Background Knowledge and Related Work}\label{chapter:Background}
%What I really want to outline here is that I am reviewing work related to a pretty narrow field - that of target detection in a forensic management scene. After giving some broader information related to multi-agent systems etc., give a narrower summary of work in this field.

\workinprogress
As mentioned in the introduction chapter, the research outlined in this thesis was motivated and funded by an EU Horizon 2020 project called ROCSAFE, which involves investigating the automation of certain aspects of the management and examination of a crime scene in the forensic stage of analysis. Accordingly, this chapter outlines existing research specifically related to the application of agent-based systems in this area, while also providing a broad overview of single and multi-agent systems and general techniques commonly used in such systems to solve abstract problems. \par
First, a synopsis of the ROCSAFE project, which funded and motivated this work is presented. Then a broad overview of agent-based systems is given, mainly outlining common approaches in agent and multi-agent system design. This leads to a more focused discussion on how agents and multi-agent systems have been designed in work that is tightly related to that of this thesis. Important concepts and algorithms relating to multi-agent probabilistic search and multi-agent coverage are then outlined. Techniques used to reach the current state-of-the-art for these problems are identified and discussed. Finally, work previously done 
%in simulating environments for systems that operate in a complex real-world scenario is appraised and reviewed.
which relates to the research questions stated in Chapter \ref{chapter:introduction} is appraised and reviewd.

\input{Chapters/BackgroundKnowledgeAndRelatedWork/ROCSAFE.tex}


\section{Agents and Multi-Agent Systems}
%talk about the usual design of multi-agent systems and the history of multi-agent systems
\input{Chapters/BackgroundKnowledgeAndRelatedWork/AgentSystemsBackground/AgentSystemsReview.tex}

\section{Multi-Agent Stochastic Target Localization}
\input{Chapters/BackgroundKnowledgeAndRelatedWork/MultiAgentTargetDetectionBackground/MultiAgentSystemsTargetDetectionBackground.tex}

\section{Multi-Agent Coverage Problem}
\input{Chapters/BackgroundKnowledgeAndRelatedWork/MultiAgentCoverageBackground/MultiAgentCoverageReview.tex}

\section{Simulation Environments}
\input{Chapters/BackgroundKnowledgeAndRelatedWork/SimulationEnvBackground/SimulationEnvironmentReview.tex}

