\chapter{High-Fidelity Simulation Environment}\label{chap:HighFidelitySim}
\workinprogress
Designing software to aid the management of a complex and dangerous scene presents many challenges, some of which may not be reasonably foreseen. As mentioned in the motivation section, hazardous events are difficult to prepare for because they tend to be rare and diverse with limited available data from real events. Physical training exercises are not frequently held due to cost, which also limits the amount of data that is available. A consequence of this is that any systems that are developed to provide support can be difficult to evaluate and validate. As outlined in the background knowledge chapter, to the best of our knowledge, there are not many simulations in existence that specifically address these kind of scenarios. To address this, we developed a high-fidelity simulated environment as part of the research involved in this thesis, which preserves the critical aspects of CBRNe incidents without presenting any risk of exposure to the dangerous elements of such scenes in the real world. The following published works related to the development of the simulation environment are discussed in this chapter: \citet{Smyth2018AInvestigation}, \citet{Smyth2018UsingDrones}.\par

\note{alternative beginning}
As highlighted in the introduction, one of the main goals of the ROCSAFE project \cite{rocsafeNUIG} is to avoid putting forensic investigators in potentially hazardous scenarios by using autonomous robots in their stead. Forensic investigations are typically complex processes, with manuals outlining best practices hundreds of pages long. This offers 


\section{Virtual Environment Design}
\input{Chapters/SimulationEnv/SimulationEvironmentDesign.tex}

\section{Virtual Aerial Vehicle Integration}
\input{Chapters/SimulationEnv/VirtualRAV.tex}

\section{Interface to Real-World Systems}
\note{This work might be better placed in multi agent coverage chapter}
%Dicuss Shiny UI, GPS system etc.

\section{Ideas For Future Work}